Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions and additions

>>>>

\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} We described concerns with model misspecification at the outset in two general dimensions: the background dataset and sampling methodology for the random graph. The differences we found from prior research in which categories demonstrated the highest hit rates were caused both by differences in the background dataset and in our sampling methodology through differences in article z-score distributions. When z-scores are shifted downward, for example, using one algorithm versus another, then the former algorithm can result in an increased percentage of HN articles. We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.
